Manifold Destiny - or how to rig an election

### 2023-12-30 presentation.qmd
bef

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
```

>>>>

```{r, echo=F, message=F, warning=F}
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
md <- ManifoldDestinyWASMD::metad
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
```
